Algorithm Selection for Graph Algorithms

### 2015-12-08 portfolio/as-graphs.Rnw
more graphs

<<echo=FALSE, message=FALSE, warning=FALSE>>=
opts_chunk$set(comment=NA, fig.width='\\textwidth', fig.height=5, fig.pos='!ht')
library(llama)
library(BBmisc)
library(xtable)
library(plyr)
library(aslib)

@@

<<echo=FALSE,fig.cap='Single best algorithm vs.\ portfolio performance (best model).'>>=
best = which.min(c(resc$mean.performance))
mod = list(modelc)[[best]]
perfScatterPlot(parscores, mod, singleBest, ldf, addCostsx = TRUE, addCostsy = FALSE, factor = 1, pargs=aes(colour = family)) + scale_x_log10() + scale_y_log10() + xlab("portfolio") + ylab("single best")
@

@@

@@

>>>>

<<echo=FALSE, message=FALSE, warning=FALSE>>=
opts_chunk$set(comment=NA, fig.width='\\textwidth', fig.height=5, fig.pos='!ht')
library(llama)
library(BBmisc)
library(xtable)
library(plyr)
library(aslib)
library(tidyr)

@@

<<echo=FALSE,fig.cap='Single best algorithm vs.\ portfolio performance (best model).'>>=
best = which.min(c(resc$mean.performance, resr$mean.performance, rescp$mean.performance, resrp$mean.performance))
mod = list(modelc, modelr, modelcp, modelrp)[[best]]
perfScatterPlot(parscores, mod, singleBest, ldf, addCostsx = TRUE, addCostsy = FALSE, factor = 1, pargs=aes(colour = family)) + scale_x_log10() + scale_y_log10() + xlab("portfolio") + ylab("single best")
@

<<echo=FALSE,fig.cap='ECDF for algorithms and portfolio (best model).'>>=
vbs.agg = aggregate(as.formula(paste("score~", paste(c("instance_id", "iteration"), sep="+", collapse="+"))), vbs(ldf), function(ss) { ss[1] })
vbs.agg$virtual.best = parscores(ldf, vbs, factor = 1)
vbs.agg$iteration = NULL
vbs.agg$score = NULL

pmod = mod$predictions
pmod$portfolio = parscores(ldf, mod, factor = 1)
pmod$iteration = NULL
pmod$algorithm = NULL
pmod$score = NULL

perfs = subset(ldf$data, TRUE, c("instance_id", ldf$performance))
perfs = merge(perfs, vbs.agg, by = "instance_id")
perfs = merge(perfs, pmod, by = "instance_id")
wide = gather_(perfs, "solver", "time", names(perfs)[-1])
ggplot(wide, aes(x = time, col = solver)) + stat_ecdf() + scale_x_log10() +
    ylab("fraction of instances solved")
@

@@

<<echo=FALSE,fig.cap='ECDF for algorithms and portfolio (best model).'>>=
vbs.agg = aggregate(as.formula(paste("score~", paste(c("instance_id", "iteration"), sep="+", collapse="+"))), vbs(ldf3), function(ss) { ss[1] })
vbs.agg$virtual.best = parscores(ldf3, vbs, factor = 1)
vbs.agg$iteration = NULL
vbs.agg$score = NULL

pmod = mod$predictions
pmod$portfolio = parscores(ldf3, mod, factor = 1)
pmod$iteration = NULL
pmod$algorithm = NULL
pmod$score = NULL

perfs = subset(ldf3$data, TRUE, c("instance_id", ldf3$performance))
perfs = merge(perfs, vbs.agg, by = "instance_id")
perfs = merge(perfs, pmod, by = "instance_id")
wide = gather_(perfs, "solver", "time", names(perfs)[-1])
ggplot(wide, aes(x = time, col = solver)) + stat_ecdf() + scale_x_log10() +
    ylab("fraction of instances solved")
@

@@

<<echo=FALSE,fig.cap='ECDF for algorithms and portfolio (best model).'>>=
vbs.agg = aggregate(as.formula(paste("score~", paste(c("instance_id", "iteration"), sep="+", collapse="+"))), vbs(ldf2), function(ss) { ss[1] })
vbs.agg$virtual.best = parscores(ldf2, vbs, factor = 1)
vbs.agg$iteration = NULL
vbs.agg$score = NULL

pmod = mod$predictions
pmod$portfolio = parscores(ldf2, mod, factor = 1)
pmod$iteration = NULL
pmod$algorithm = NULL
pmod$score = NULL

perfs = subset(ldf2$data, TRUE, c("instance_id", ldf2$performance))
perfs = merge(perfs, vbs.agg, by = "instance_id")
perfs = merge(perfs, pmod, by = "instance_id")
wide = gather_(perfs, "solver", "time", names(perfs)[-1])
ggplot(wide, aes(x = time, col = solver)) + stat_ecdf() + scale_x_log10() +
    ylab("fraction of instances solved")
@
